---
title: "praat_textgrid_to_csv"
author: "blind"
date: "2023-11-08"
output: html_document
---

```{r setup, include=FALSE}

library(xml2)
library(dplyr)
library(readr)
library(tidyr)
library(tidyverse)
```


```{r}
#this is the name after user we used last week
#if you do not know then use the function on the next line by removing the #
#getwd()
your_name<-"adambramlett"
dir<-file.path("/Users",your_name,"scripts/music_project_23/ppcc_iflu_data/Exp1/AllSentences/")
dir
list.files(dir)
tgs<-list.files(dir,pattern = ".TextGrid",full.names = TRUE)
#if this next line comes up as (0)characters then your name is wrong
#tgs
dum<-read.csv(tgs[1],sep = "")
cols<-ncol(dum)+1
#cols

#pull data
data <- data.frame(matrix(ncol = cols, nrow = 0))
for (files in 1:length(tgs)){
  dum<-read.csv(tgs[files],sep = "")
  dum$name<-tgs[files]
  data<-rbind(data,dum)
} 

#clean data
data_c<-data%>%
  mutate(file_name_ext=str_split(data$name,"/(?=[^/]+$)",simplify = T)[, 2])

data_c1<-data_c%>%
  mutate(file_name=str_split(data_c$file_name_ext,pattern = "[.]",simplify = T)[, 1],
         textgrid = ooTextFile)%>%
  select(!c(name,file_name_ext,ooTextFile))%>%
  mutate(tier = if_else(File == "item",type,""))

data_c1$tier<-str_replace_all(data_c1$tier,"\\[|\\]|\\:","")


#####Ding's solution - empty doesnt mean ""
# you may need to replace if_else() with ifelse()
data_c1<-data_c1%>%
  mutate(tier = if_else(textgrid == "TextGrid","0",tier))%>%
  mutate(tier = if_else(tier == "",NA,tier),
         textgrid = if_else(tier == "",NA,textgrid))%>%
  fill(tier,.direction="down")%>%
  fill(textgrid,.direction="down")%>%
  filter(textgrid != "TextGrid",
         File != "item")%>%
  select(!c(textgrid))%>%
  mutate(transcribe_point = if_else(X. == "IntervalTier","0",if_else(File == "intervals",type,NA)))

data_c1$transcribe_point<-str_replace_all(data_c1$transcribe_point,"\\[|\\]|\\:","")


data_c1_wider<-data_c1%>%
  fill(transcribe_point,.direction="down")%>%
  filter(File == "xmin"|File == "xmax"|File == "text")%>%
  mutate(transcribed_info = if_else(File == "text",X.,NA))%>%
  fill(transcribed_info,.direction = "up")%>%
  filter(File != "text")%>%
  filter(transcribed_info != "")%>%
  select(!type)%>%
  pivot_wider(names_from = File,values_from=X.)

#View(data_c1_wider)
#write.csv(data_c1_wider,file.path(dir,"text_grid_info.csv"))
```

```{r}
data_c1_wide_wide<-data_c1_wider%>%
  select(-transcribe_point)%>%
  pivot_wider(
    names_from = transcribed_info,
    values_from = c(xmin, xmax),
    names_sep = "_")

agg<-data_c1_wider%>%group_by(file_name)%>%count()
head(data_c1_wider)
```

```{r}
#check to see if all files are there
dir<-file.path("/Users",your_name,"scripts/music_project_23/ppcc_iflu_data/Exp1/AllSentences/")
dir
list.files(dir)
tgs2<-list.files(dir,pattern = ".wav")
#if this next line comes up as (0)characters then your name is wrong
#cols

#pull data
datas <- data.frame(tgs2)

datas<-datas%>%
  mutate(file_name = str_replace_all(tgs2, ".wav", ""))

all_data<-datas%>%left_join(data_c1_wide_wide)
```

```{r}
library(readr)
library(dplyr)
library(purrr)

your_name<-"adambramlett"
csv_dir<-file.path("/Users",your_name,"scripts/music_project_23/ppcc_iflu_data/Exp1/csvs/")
list.files(csv_dir)

file_names <- list.files(path = csv_dir, pattern = "\\.csv$", full.names = TRUE)

list<-list.files(path = csv_dir, pattern = "\\.csv$", full.names = TRUE)

dum<-read.csv(list[1],sep = "")
cols<-ncol(dum)+1

# Function to read each file and add a column with the file name
data <- data.frame(matrix(ncol = cols, nrow = 0))
for (files in 1:length(list)){
  dum<-read.csv(list[files],sep = "")
  dum$name<-list[files]
  data<-rbind(data,dum)
} 

data_full<-data%>%
  mutate(file_name = str_replace_all(name, csv_dir, ""))%>%
  mutate(file_name = str_replace_all(file_name, "/", ""))%>%
  mutate(file_name = str_replace_all(file_name, ".wav", ""))%>%
  mutate(file_name = str_replace_all(file_name, ".csv", ""))%>%
  select(-name)%>%
  left_join(data_c1_wide_wide)

p_ref <- 2e-5  # 20 micropascals
View(data_full)
colnames(data_full)

data_full_clean<-data_full%>%
  filter(time>xmin_v1 & time<xmax_v1|time>xmin_v2 & time<xmax_v2)%>%
  filter(pitch!=0)%>%
  mutate(vowel=case_when(time>xmin_v1 & time<xmax_v1~"v1",
                         time>xmin_v2 & time<xmax_v2~"v2"),
         vowel=as.factor(vowel))%>%
  select(-c(xmin_v1,xmax_v1,xmin_v2,xmax_v2))%>%
    separate(
      file_name, into = c("word", "stress"), sep = "_")%>%
  mutate(stress=if_else(stress=="p","penultimate","antipenultimate"))%>%
  mutate(time=as.numeric(time),
         pitch=as.numeric(pitch),
         intensity=as.numeric(intensity),
         formant1=as.numeric(formant1),
         formant2=as.numeric(formant2),
         formant3=as.numeric(formant3),
         amplitude = p_ref * 10^(intensity/20))%>%
  group_by(word, vowel)%>% 
  mutate(relative_time = time - min(time) + 1) %>%
  ungroup()%>%
  mutate(
    energy_f1 = 10^(intensity/10) * formant1,
    energy_f2 = 10^(intensity/10) * formant2,
    energy_f3 = 10^(intensity/10) * formant3,
    spectral_tilt = energy_f1/(energy_f1+energy_f2+energy_f3))

```
```{r}
data_full_clean%>%ggplot(aes(y=pitch,x=relative_time,color=stress,alpha=.3))+
  geom_jitter()+
  facet_grid(vowel~.)

data_full_clean%>%ggplot(aes(y=intensity,x=relative_time,color=stress,alpha=.3))+
  geom_jitter()+
  facet_grid(vowel~.)

data_full_clean%>%ggplot(aes(y=amplitude,x=relative_time,color=stress,alpha=.3))+
  geom_jitter()+
  facet_grid(vowel~.)

data_full_clean%>%ggplot(aes(y=formant1,x=relative_time,color=stress,alpha=.3))+
  geom_jitter()+
  facet_grid(vowel~.)

data_full_clean%>%ggplot(aes(y=formant2,x=relative_time,color=stress,alpha=.3))+
  geom_jitter()+
  facet_grid(vowel~.)

data_full_clean%>%ggplot(aes(y=formant3,x=relative_time,color=stress,alpha=.3))+
  geom_jitter()+
  facet_grid(vowel~.)
```

```{r}
data_full_clean_agg<-data_full_clean%>%
  group_by(word,vowel,stress)%>%
  summarise(mean_pitch=max(pitch),
            mean_amplitude=mean(amplitude),
            min_time=min(relative_time),
            max_time=max(relative_time),
            duration=max_time-min_time,
            mean_tilt=mean(spectral_tilt))

View(aco_agg)
aco_agg<-data_full_clean_agg%>%
  group_by(stress,vowel)%>%
  na.omit()%>%
  summarize(mean_pitch=mean(mean_pitch),
            mean_amplitude=mean(mean_amplitude),
            mean_dur=mean(duration)*1000,
            mean_tilt=mean(mean_tilt))
#previous code
#all_data<-data_full_clean_agg%>%left_join(spec_tilt_clean)
all_data<-data_full_clean_agg
write.csv(all_data,"acoustic_data_ppcc.csv")
```

```{r}
# Load necessary libraries
library(tuneR)

# Directory where the .wav files are located
directory <- "../../ppcc_iflu_data/Exp1/files"

# List all .wav files in the directory
wav_files <- list.files(directory, pattern = ".wav", full.names = TRUE)

# Initialize a data frame to store file names and durations
file_data <- data.frame(
  file_name = character(),
  duration_ms = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each .wav file and get its duration in milliseconds
for (wav_file in wav_files) {
  # Read the .wav file
  audio <- readWave(wav_file)
  
  # Get the duration in milliseconds
  duration_ms <- length(audio@left) / audio@samp.rate * 1000
  
  # Append the file name and duration to the data frame
  file_data <- rbind(file_data, data.frame(file_name = basename(wav_file), duration_ms = duration_ms))
}


mean_duration <- mean(file_data$duration_ms)

# Calculate the standard deviation of the durations in milliseconds
sd_duration <- sd(file_data$duration_ms)

```


#previous code
```{r}
path<-list.files("../../ppcc_iflu_data/Exp1/AllSentences",pattern = ".txt",full.names=TRUE)
path
spec_tilt_v2<-read.delim(path[3])%>%mutate(syllable="v2")
spec_tilt_v1<-read.delim(path[2],delim="\t")%>%mutate(syllable="v1")

path[3]
path[2]
View(spec_tilt_v2)

spec_tilt<-rbind(spec_tilt_v1,spec_tilt_v2)
View(spec_tilt)

clean_colnames <- function(df) {
  colnames(df) <- gsub("^X1", "", colnames(df))
  return(df)
}

spec_tilt <- clean_colnames(spec_tilt)

spec_tilt_clean<-spec_tilt%>%
  filter(label != "label")%>%
  select(-X)%>%
  mutate(
    H1_H2 =  as.numeric(H1dB) / -as.numeric(H2dB),
    H1_A1 = as.numeric(F1) / as.numeric(F3),
    H1_A2 = as.numeric(A3dB) / as.numeric(A1dB) ,
    H1_A3 = as.numeric(A3dB) / as.numeric(H1dB),
    H1.H2=as.numeric(H1.H2),
    H1_A3 = as.numeric(A3dB) / as.numeric(H1dB))%>%
  mutate(vowel=syllable)%>%
  separate(label, into = c("word", "stress"), sep = "_")%>%
  select(-c(syllable))

spec_agg<-spec_tilt_clean%>%
  group_by(stress,vowel)%>%
  na.omit()%>%
  summarize(mean_tilt1=mean(H1_H2),
            mean_tilt2=mean(H1_A1),
            mean_tilt3=mean(H1_A2),
            mean_tilt4=mean(H1_A3),
            mean_tilt5=mean(H1.H2))

```

# Extracts mean formant values, H1, H2, and spectral tilt measures
# dynamically across an duration defined by the textgrid. 
# The number of interval values extracted is equal to numintervals below.
# Writes results to a textfile.
# Christian DiCanio, 2007 - revised 2008 to include output amplitude values.
# Revised in 2012 to work iteratively across a directory.
# Note that LTAS bin is set to 50 Hz.

numintervals = 1
#Number of intervals you wish to extract pitch from.

form Extract Formant data from labelled points
   sentence Directory_name: /Users/adambramlett/scripts/music_project_23/ppcc_iflu_data/Exp1/files/
   sentence Interval_label 1
   sentence Log_file data2
   positive Labeled_tier_number 1
   positive Analysis_points_time_step 0.005
   positive Record_with_precision 1
   comment Formant Settings:
   positive Analysis_time_step 0.005
   positive Maximum_formant 5000
   positive Number_formants 3
   positive F1_ref 500
   positive F2_ref 1485
   positive F3_ref 2450
   positive F4_ref 3550
   positive F5_ref 4650
   positive Window_length 0.005
   comment Pitch Settings:
   positive Octave_cost 0.01
   positive Pitch_floor 80
   positive Pitch_ceiling 300
endform

maxf =maximum_formant

# If your sound files are in a different format, you can insert that format instead of wav below.
# Resampling done for LPC analysis.

Create Strings as file list... list 'directory_name$'/*.wav
num = Get number of strings
for ifile to num
	select Strings list
	fileName$ = Get string... ifile
	Read from file... 'directory_name$'/'fileName$'
	soundID1$ = selected$("Sound")
	Resample... 16000 50
	soundID2 = selected("Sound")
	Read from file... 'directory_name$'/'soundID1$'.TextGrid
	textGridID = selected("TextGrid")
	num_labels = Get number of intervals... labeled_tier_number

fileappend 'directory_name$''log_file$'.txt label'tab$'

for i to numintervals
	fileappend 'directory_name$''log_file$'.txt 'i'F1'tab$''i'F2'tab$''i'F3'tab$'
	fileappend 'directory_name$''log_file$'.txt 'i'H1hz'tab$''i'H2hz'tab$''i'hnr'tab$'
	fileappend 'directory_name$''log_file$'.txt 'i'H1-H2'tab$''i'H1dB'tab$''i'H2dB'tab$''i'H1-A1'tab$''i'A1dB'tab$''i'H1-A2'tab$''i'A2dB'tab$''i'H1-A3'tab$''i'A3dB'tab$'
endfor
fileappend 'directory_name$''log_file$'.txt 'newline$'


for i to num_labels
	select 'textGridID'
	label$ = Get label of interval... labeled_tier_number i
		if label$ = interval_label$
			fileappend 'directory_name$''log_file$'.txt 'fileName$''tab$'
      			intvl_start = Get starting point... labeled_tier_number i
			intvl_end = Get end point... labeled_tier_number i
			select 'soundID2'
			Extract part... intvl_start intvl_end Rectangular 1 no
			intID = selected("Sound")	
			To Pitch (ac)...  'analysis_points_time_step' 'pitch_floor' 15 no  0.03 0.45 'octave_cost' 0.35 0.14 'pitch_ceiling'
			invl_pitch = selected("Pitch")
			select 'intID'
			To Harmonicity (cc)... 'analysis_points_time_step' 'pitch_floor' 0.1 4.5
			invl_hnr = selected("Harmonicity")
			chunkID  = (intvl_end-intvl_start)/numintervals

			for j to numintervals

				#Getting formants and frequency boundaries 10% away from them. Writing to data file.

				select 'intID'
				Extract part... (j-1)*chunkID j*chunkID Rectangular 1 no
				chunk_part = selected("Sound")
				form_chunk = To Formant (burg)... 0 5 'maxf' 'window_length' 50
				formantID_bf = selected("Formant")
				Track... 'number_formants' 'f1_ref' 'f2_ref' 'f3_ref' 'f4_ref' 'f5_ref' 1 1 1
				formantID = selected("Formant")
				f1 = Get mean... 1 0 0 Hertz
				f1_a = f1-(f1/10)
				f1_b = f1+(f1/10)
				f2 = Get mean... 2 0 0 Hertz
				f2_a = f2-(f2/10)
				f2_b = f2+(f2/10)
				f3 = Get mean... 3 0 0 Hertz
				f3_a = f3-(f3/10)
				f3_b = f3+(f3/10)
					if j = numintervals
					fileappend 'directory_name$''log_file$'.txt
 	           			... 'f1''tab$''f2''tab$''f3'
					else
					fileappend 'directory_name$''log_file$'.txt
   	         			... 'f1''tab$''f2''tab$''f3'
					endif
				select 'intID'
				select 'formantID_bf'
				select 'formantID'
				Remove

				#Getting H1 and H2 values by extracting pitch values. Then getting the frequency
				#boundaries 10% away from them. Writes H1 and H2 measures to data file.

				select 'invl_pitch'
				h1hz = Get mean... (j-1)*chunkID j*chunkID Hertz
				h1hz_a = h1hz-(h1hz/10)
				h1hz_b = h1hz+(h1hz/10)
				h2hz = h1hz*2
				h2hz_a = h2hz-(h2hz/10)
				h2hz_b = h2hz+(h2hz/10)
					if j = numintervals
					fileappend 'directory_name$''log_file$'.txt
 	           			... 'tab$''h1hz''tab$''h2hz'
					else
					fileappend 'directory_name$''log_file$'.txt
   	         			... 'tab$''h1hz''tab$''h2hz'
					endif

				select 'invl_hnr'			
				hnr = Get mean... (j-1)*chunkID j*chunkID
					if j = numintervals
					fileappend 'directory_name$''log_file$'.txt
 	           			... 'tab$''hnr'
					else
					fileappend 'directory_name$''log_file$'.txt
   	         			... 'tab$''hnr'
					endif


				#Converting each chunk in interval to a long term average spectrum. Then queries
				#the maximum amplitude within a frequency region specified by the frequency
				#boundaries around H1, H2, F1, F2, and F3. The difference between these maxima
				#is a measure of spectral tilt which is then written to the data file.

				select 'chunk_part'
				To Ltas... 50
				ltasID = selected("Ltas")
				h1db = Get maximum... h1hz_a h1hz_b None
				h2db = Get maximum... h2hz_a h2hz_b None
				a1db = Get maximum... f1_a f1_b None
				a2db = Get maximum... f2_a f2_b None
				a3db = Get maximum... f3_a f3_b None
				h1_h2 = h1db - h2db
				h1_a1 = h1db - a1db
				h1_a2 = h1db - a2db
				h1_a3 = h1db - a3db
					if j = numintervals
					fileappend 'directory_name$''log_file$'.txt
 	           			... 'tab$''h1_h2''tab$''h1db''tab$''h2db''tab$''h1_a1''tab$''a1db''tab$''h1_a2''tab$''a2db''tab$''h1_a3''tab$''a3db''newline$'
					else
					fileappend 'directory_name$''log_file$'.txt
   	         			... 'tab$''h1_h2''tab$''h1db''tab$''h2db''tab$''h1_a1''tab$''a1db''tab$''h1_a2''tab$''a2db''tab$''h1_a3''tab$''a3db''tab$'
					endif
				select 'ltasID'
				Remove
			endfor
		select 'intID'
		Remove
		select 'invl_pitch'
		Remove
		else
			#do nothing
   		endif
endfor
endfor
select all
Remove
